### 2025-11-12 Tables/investment_table.tex
fix investment table
add CEO analysis graphs

\caption{\label{tab:investment}Effect of Clinically Trained Executive on Hospital-Level Expenses}
\centering
\begin{tabular}[t]{lccclc}
\toprule
 & Moveable Equip. & Fixed Equipment & Labor Costs & Building Purchases & Total Expenses\\
\midrule
Clinical Exec x Post 2012 & -1 & 6.95 & -1.37 & 0.56 & 1.83\\
 & (2.05) & (6.14) & (2.22) & (7.28) & (8.75)\\
 &  &  &  &  & \\
Observations & 1,532 & 660 & 1,670 & 1,435 & 2,485\\
\bottomrule
\multicolumn{6}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{6}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:investment}Effect of Clinically Trained Executive on Hospital-Level Expenses}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
 & Nurses & Moveable Equip & Fixed Equip & Labor & Building & Total\\
\midrule
Clinical Exec x Post 2012 & 9.08 & -1 & 6.95 & -1.37 & 0.56 & 1.83\\
 & (8.1) & (1.83) & (6.78) & (2.38) & (7.42) & (8.18)\\
 &  &  &  &  &  & \\
Observations & 2,485 & 1,532 & 660 & 1,670 & 1,435 & 2,485\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}
